Field work 2016

### 2016-12-07 analysis/geo2.Rmd
add geospatial analysis add notes dendro

```{r readData}
# mymachine <- '/Users/ajpeluLap/' 
mymachine <- '/Users/ajpelu/' 
di <- paste0(mymachine, 'Dropbox/phd/phd_repos/qpyr_dendro/')

@@

@@

mig <- spTransform(mig, CRS("+init=epsg:4236"))
ots <- spTransform(ots, CRS("+init=epsg:4236"))

@@

  # Layers control
  addLayersControl(position = 'bottomright',
                   # baseGroups = c("Topographical","Ortophotography 2009","PNOA"),
                   baseGroups = c("Ortophotography 2009", "Topographical"),
                   overlayGroups = c("Migrame", "OBSNEV Fen", "Gea Izquierdo 2014"),
                   options = layersControlOptions(collapsed = FALSE))

@@

mymap %>% 
  fitBounds(myext@xmin, myext@ymin, myext@xmax, myext@ymax) %>% 
  addPolylines(data=mig_forest_sj, color='blue', group='Migrame', popup=mig_forest_sj$nombre) %>% 
  addCircles(ots_phe, 
             lng=coordinates(ots_phe)[,'x'], 
             lat=coordinates(ots_phe)[,'y'], 
             group='OBSNEV Fen', radius=2, color = 'red', popup=ots_phe$name) %>% 
  addCircles(ots_gea, 
             lng=coordinates(ots_gea)[,'x'], 
             lat=coordinates(ots_gea)[,'y'], 
             group='Gea Izquierdo 2014', radius=2, color = 'green', popup=ots_gea$name)

@@

mymap %>% 
  fitBounds(myext@xmin, myext@ymin, myext@xmax, myext@ymax) %>% 
  addPolylines(data=mig_forest_ca, color='blue', group='Migrame', popup=mig_forest_ca$nombre) %>% 
  addCircles(ots_phe, 
             lng=coordinates(ots_phe)[,'x'], 
             lat=coordinates(ots_phe)[,'y'], 
             group='OBSNEV Fen', radius=2, color = 'red', popup=ots_phe$name) %>% 
  addCircles(ots_gea, 
             lng=coordinates(ots_gea)[,'x'], 
             lat=coordinates(ots_gea)[,'y'], 
             group='Gea Izquierdo 2014', radius=2, color = 'green', popup=ots_gea$name)

>>>>

```{r readData}
mymachine <- '/Users/ajpeluLap/' 
# mymachine <- '/Users/ajpelu/' 
di <- paste0(mymachine, 'Dropbox/phd/phd_repos/qpyr_dendro/')

@@

# field woek points 
fw <- readOGR(paste0(di, 'data_raw/geoinfo/'), layer = 'dendro_garmin', verbose = FALSE)

@@

# Reproject 
mig <- spTransform(mig, CRS("+init=epsg:4236"))
ots <- spTransform(ots, CRS("+init=epsg:4236"))
fw <- spTransform(fw, CRS("+init=epsg:4236"))

@@

  # Layers control
  addLayersControl(position = 'bottomright',
                   # baseGroups = c("Topographical","Ortophotography 2009","PNOA"),
                   baseGroups = c("Ortophotography 2009", "Topographical"),
                   overlayGroups = c("Field Work 2016", "Migrame", "OBSNEV Fen", "Gea Izquierdo 2014"),
                   options = layersControlOptions(collapsed = FALSE))
```

@@

mymap %>% 
  fitBounds(myext@xmin, myext@ymin, myext@xmax, myext@ymax) %>% 
  addPolylines(data=mig_forest_sj, color='blue', group='Migrame', popup=mig_forest_sj$nombre) %>% 
  addCircles(ots_phe, 
             lng=coordinates(ots_phe)[,'x'], 
             lat=coordinates(ots_phe)[,'y'], 
             group='OBSNEV Fen', radius=2, color = 'red', popup=ots_phe$name) %>% 
  addCircles(ots_gea, 
             lng=coordinates(ots_gea)[,'x'], 
             lat=coordinates(ots_gea)[,'y'], 
             group='Gea Izquierdo 2014', radius=2, color = 'green', popup=ots_gea$name) %>% 
  addCircles(fw, 
             lng=coordinates(fw)[,'coords.x1'], 
             lat=coordinates(fw)[,'coords.x2'], 
             group='Field Work 2016', radius=2, color = 'yellow', popup=fw$name)

@@

mymap %>% 
  fitBounds(myext@xmin, myext@ymin, myext@xmax, myext@ymax) %>% 
  addPolylines(data=mig_forest_ca, color='blue', group='Migrame', popup=mig_forest_ca$nombre) %>% 
  addCircles(ots_phe, 
             lng=coordinates(ots_phe)[,'x'], 
             lat=coordinates(ots_phe)[,'y'], 
             group='OBSNEV Fen', radius=2, color = 'red', popup=ots_phe$name) %>% 
  addCircles(ots_gea, 
             lng=coordinates(ots_gea)[,'x'], 
             lat=coordinates(ots_gea)[,'y'], 
             group='Gea Izquierdo 2014', radius=2, color = 'green', popup=ots_gea$name) %>% 
  addCircles(fw, 
             lng=coordinates(fw)[,'coords.x1'], 
             lat=coordinates(fw)[,'coords.x2'], 
             group='Field Work 2016', radius=2, color = 'yellow', popup=fw$name)
```
